The prospects for human-based inspection of the vast number of images to be
produced by the Rubin/LSST are unavoidably going to be limited to a 
fraction of the dataset produced (even nightly, let alone for the full 10-year
survey).  Yet, the potential value of getting human eyes on the images (including
the raw, minimally processed, and final processed and calibrated stages), is
immense, in particular for identifying patterns that are easily spotted by eye,
yet tend to evade most modern automated image quality assessment protocols.

Every dataset from any given observation program comes with its own unique set
of ``features'' stemming from the observatory structures, optics, camera,
detectors, electronics, observation strategy, the night sky, calibration products, 
etc.  This makes eyeball inspection particularly valuable in the early days of 
commissioning.  Fortuitously, the energy and enthusiasm of internal project members
are at extrememly high levels at this stage, so there is no shortage of voluntary
effort for human visial inpsection for the commissioning phase of the \ComCam.
This effort to date has largely proceded via an informal
see-something-say-something scheme, with many users posting their latest findings
on the internal staff Slack channels (namely the \#sciunit-image-inspection channel,
but also prominently in other channels, \#sciunit-lsb, \#validation-team,
\#embargo-beautiful-images, \#ops-satellites, \#dm-calibraion-products to name a few).

Anomolies and peculiarities reported to date along with details of and/or pointers
to further study and explanation (where applicable) include:
\begin{itemize}

\item \textbf{ghosts}: most prominent around bright stars (including those falling
  outside of the FOV) and attributed to multi-bounce reflections off of the focal
  plane and the \ComCam optics.  Qualitatively, the presence and appearance of 
  the ghosts are well predicted by Josh Meyers' ``batoid ray tracer'', even in its
  current unoptimized state.  It is noted that the nature of the ghosts will be
  quite different for the full LSSTCam, but this initial level of understanding
  of this feature is promissing and useful for honing characterization and
  mitigation strategies.

\item \textbf{stray/scattered light}: prominent ring-shaped waffle/corduroy-like
  features seen early on were identified as originating from a blinking light on a
  crane that was left on. Large irregular ring-shaped ``spots'' were attributed to
  the laser tracker (an issue in access to turn it off was noted). \ComCam is 
  known to be less well baffled than LSSTCam, so scattered light from off-axis light 
  sources is expected to be worse.

\item \textbf{satellite streaks}: see Section~\ref{sec:dia_transient_variable}

\item \textbf{kettlebell \& trefoil-shaped PSFs}: see Section~\ref{sec:aos_commissioning}.
  This issue was further investigated in the context of the PSF modelling itself on such
  irregularly shaped PSFs.  It was noted that the preferred ``piff'' algorigthm (which
  is used for the final characterization model) was performing worse that the ``psfex''
  algorithm (which, due to its relative speed, is used in the initial characterization).
  As such, we temporarily switched to using only ``psfex'' until the image quality was
  improved.  Given the incredible and expeditious work of the AOS team, we are already
  confident that we can switch back to our preferred configurartion.  (This has also
  spurred a study into the reason why ``piff'' seems to struggle with these shapes and
  will hopefully lead to improvements there, see
  Section~\ref{sec:delivered_image_quality_and_psf}).

\item \textbf{background subtraction issues}: see Section~\ref{sec:low_surface_brightness}

\item \textbf{repeated patchwork gradients}: a small number of images appear to have a 
  bias gradient that appears in several amplifiers of detector 1 (R00\_S01). This feature 
  is currently under investigation, but it appears to be most prominent when a bright star 
  resides close to the amplifier (right) edge of this detector. The bias shift appears in 
  the prescan, active area, and overscan regions of the affected amplifiers. It seems 
  likely that this is some type of crosstalk, but the origin and manifestation is unclear. 
  It remains to be seen whether similar features are seen in any other detectors. It is 
  likely that this feature will be further studied in the context of Section~\ref{sec:isr}.

\item \textbf{trailed sources}: due to tracking errors.  These are particularly
  difficult to identify with automated image quality metrics (there are some ideas
  about using AI to identify tracking error-based image degradation floating around,
  but we also hope to be able to confidently rely on data from the EDF to indicate
  tracking issues).

\end{itemize}

\noindent \textbf{Future Endeavors}

A major goal for future image inspction efforts is to develop a more systematic
way to identify and report issues and, where possible, alert the
relevant stakeholders for further investigations into mitigating problems.

There has been some effort to deploy the ``Exposure Checker'' that was developed for the Dark Energy Survey \citep{2016A&C....16...99M}\footnote{See demo \url{https://des-exp-checker.pmelchior.net/}} and has been previously deployed by LSST DESC for the visual inspection of simulated DC2 data \citep{2021ApJS..253...31L}.

Also recently implemented for visual inspection is a rendering of the 3-color coadd
HIPS maps produced regularly during the nightly validation and DRP processing runs.
Such images are invaluable for highlighting myriad issues at the coadd level (often
indicating a need to drill-down to the visit-level for a full diagnosis, while
providing significant clues on where to look first).
